\documentclass[12pt,a4paper]{report}

% ── Packages ──────────────────────────────────────────────────────────────────
\usepackage[margin=2.5cm]{geometry}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{titlesec}
\usepackage{titletoc}
\usepackage{fancyhdr}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{fontenc}
\usepackage{inputenc}
\usepackage{microtype}
\usepackage{tcolorbox}
\usepackage{tabularx}
\usepackage{multirow}
\usepackage{amsmath}
\usepackage{float}
\usepackage{parskip}

% ── Colours ───────────────────────────────────────────────────────────────────
\definecolor{primary}{HTML}{1A1A2E}
\definecolor{accent}{HTML}{E94560}
\definecolor{secondary}{HTML}{16213E}
\definecolor{lightgray}{HTML}{F5F5F5}
\definecolor{midgray}{HTML}{CCCCCC}
\definecolor{textgray}{HTML}{555555}

% ── Hyperref ──────────────────────────────────────────────────────────────────
\hypersetup{
  colorlinks=true,
  linkcolor=accent,
  urlcolor=accent,
  pdftitle={SalonSync - Project Proposal},
  pdfauthor={JDJ Solutions}
}

% ── Section Styling ───────────────────────────────────────────────────────────
\titleformat{\chapter}[block]
  {\normalfont\huge\bfseries\color{primary}}
  {\thechapter.}{1em}{}
  [\vspace{2pt}{\color{accent}\rule{\linewidth}{2pt}}]

\titleformat{\section}
  {\normalfont\Large\bfseries\color{secondary}}
  {\thesection}{1em}{}

\titleformat{\subsection}
  {\normalfont\large\bfseries\color{textgray}}
  {\thesubsection}{1em}{}

% ── Header / Footer ───────────────────────────────────────────────────────────
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\small\color{textgray}SalonSync — Project Proposal}
\fancyhead[R]{\small\color{textgray}JDJ Solutions}
\fancyfoot[C]{\small\color{textgray}\thepage}
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{0pt}

% ── Highlight Box ─────────────────────────────────────────────────────────────
\tcbuselibrary{skins,breakable}
\newtcolorbox{infobox}[1][]{
  colback=lightgray, colframe=accent, arc=4pt,
  boxrule=1pt, left=6pt, right=6pt, top=6pt, bottom=6pt,
  title=#1, fonttitle=\bfseries\color{white},
  coltitle=white, attach boxed title to top left={yshift=-2mm,xshift=4mm},
  boxed title style={colback=accent,arc=3pt,boxrule=0pt}
}

% ══════════════════════════════════════════════════════════════════════════════
\begin{document}

% ── TITLE PAGE ────────────────────────────────────────────────────────────────
\begin{titlepage}
  \pagecolor{primary}
  \color{white}
  \centering
  \vspace*{3cm}

  {\fontsize{52}{60}\selectfont\bfseries Salon\textcolor{accent}{Sync}}\\[0.5cm]
  {\Large\color{midgray} Professional Salon Booking \& Management Platform}\\[2cm]

  {\color{accent}\rule{10cm}{1.5pt}}\\[1.5cm]

  {\large\bfseries Project Proposal}\\[0.3cm]
  {\normalsize Version 1.0 — April 2026}\\[2cm]

  \begin{tabular}{rl}
    \textbf{Prepared by:}  & JDJ Solutions                        \\[4pt]
    \textbf{Project Type:} & SaaS Web Application                 \\[4pt]
    \textbf{Stage:}        & Phase 1 — MVP                        \\[4pt]
    \textbf{Target Market:}& Medium-Sized Salons (Sri Lanka)      \\[4pt]
    \textbf{Pricing Model:}& 14-Day Free Trial + 2,500 LKR/month  \\
  \end{tabular}

  \vfill
  {\small\color{midgray} Confidential — For Internal Use Only}
\end{titlepage}

\pagecolor{white}\color{black}

% ── TABLE OF CONTENTS ─────────────────────────────────────────────────────────
\tableofcontents
\thispagestyle{empty}
\newpage

% ══════════════════════════════════════════════════════════════════════════════
\chapter{Executive Summary}

SalonSync is a professional-grade, serverless salon management platform purpose-built
for medium-sized salons that currently rely on manual phone calls and paper-based
scheduling. The platform directly solves the \textit{"Double-Booking Dilemma"} by
synchronising real-time customer web bookings with an intuitive digital dashboard
for salon staff.

\begin{infobox}[Mission Statement]
To empower every local salon owner with enterprise-grade scheduling technology,
delivered at zero setup cost, so they can focus on their craft — not their calendar.
\end{infobox}

The system follows a \textbf{Zero-Setup Cost} model, removing the financial barrier
for local business owners. A \textbf{14-day free trial} provides risk-free onboarding,
followed by a low-cost subscription of \textbf{2,500 LKR per month}. The architecture
is \textbf{SaaS-Ready} — while Phase 1 focuses on perfecting the single-salon
experience, the underlying design scales effortlessly to hundreds of locations.

\section{Key Business Outcomes}

\begin{itemize}[leftmargin=2em]
  \item \textbf{Eliminate double-bookings} through real-time slot locking.
  \item \textbf{Reduce no-shows} by up to 60\% via automated SMS/WhatsApp reminders.
  \item \textbf{Capture 24/7 bookings} without a receptionist.
  \item \textbf{Build a digital customer database} from day one.
  \item \textbf{Provide actionable analytics} on revenue, peak hours, and stylist performance.
\end{itemize}

% ══════════════════════════════════════════════════════════════════════════════
\chapter{Problem Statement}

\section{The Current Landscape}

The majority of medium-sized salons in Sri Lanka operate their appointment management
through a combination of:

\begin{itemize}[leftmargin=2em]
  \item Manual phone calls to accept bookings.
  \item Physical appointment books or basic WhatsApp messages.
  \item Verbal scheduling between stylists and receptionists.
\end{itemize}

This approach creates significant operational inefficiencies and directly impacts
customer experience and business revenue.

\section{Core Pain Points}

\begin{longtable}{>{\bfseries}p{4cm} p{10cm}}
  \toprule
  \textbf{Problem} & \textbf{Business Impact} \\
  \midrule
  \endfirsthead
  \multicolumn{2}{c}{\textit{Continued from previous page}} \\
  \toprule
  \textbf{Problem} & \textbf{Business Impact} \\
  \midrule
  \endhead
  \bottomrule
  \endfoot

  Double Bookings     & Two clients booked for the same stylist at the same time, causing customer loss and reputational damage. \\[6pt]
  No-Shows            & Clients forget appointments; the slot is wasted with no revenue generated. \\[6pt]
  After-Hours Missed  & Calls made after business hours result in lost bookings to competitors. \\[6pt]
  Staff Confusion     & No centralised view of the day's schedule leads to miscommunication. \\[6pt]
  No Customer Records & Walk-in clients are never followed up on, preventing loyalty building. \\[6pt]
  Manual Workload     & Receptionists spend hours per week managing calls instead of serving clients. \\
\end{longtable}

\section{The Opportunity}

Sri Lanka's beauty industry is growing rapidly, yet digital adoption among independent
salons remains critically low. SalonSync occupies a unique position: it delivers
enterprise-level scheduling capability at a price point accessible to any independent
salon owner, with zero technical knowledge required to operate.

% ══════════════════════════════════════════════════════════════════════════════
\chapter{Product Overview}

\section{Platform Vision}

SalonSync operates as a dual-interface platform:

\begin{enumerate}[leftmargin=2em]
  \item \textbf{Customer Booking Portal} — A public-facing, mobile-first web application
        where clients discover the salon, browse services, choose a stylist, and confirm
        a booking instantly.
  \item \textbf{Admin Management Dashboard} — A private, staff-only control centre
        for viewing schedules, managing walk-in bookings, tracking staff leave, and
        accessing analytics.
\end{enumerate}

\section{Main Features}

\subsection{Smart Cutter Slot System}

A dynamic scheduling engine that manages the real-time availability of up to three
hair stylists simultaneously. The system enforces atomic slot locking to ensure no
two clients can ever book the same stylist at the same time. Time slots are fixed at
\textbf{30-minute intervals} and displayed in a clean visual grid.

Key behaviours:
\begin{itemize}[leftmargin=2em]
  \item Real-time slot invalidation after each booking.
  \item Configurable working hours per stylist.
  \item Automatic slot-blocking for staff leave days.
  \item Support for back-to-back services spanning multiple slots.
\end{itemize}

\subsection{Unified Admin Dashboard}

A simplified, mobile-responsive control centre for salon staff:

\begin{itemize}[leftmargin=2em]
  \item \textbf{Grid View} — A day-at-a-glance schedule showing all stylists and
        their booked slots colour-coded by status.
  \item \textbf{Manual Booking} — Staff can add walk-in clients directly from the
        dashboard without requiring a customer-facing booking.
  \item \textbf{Leave Management} — Mark specific stylists as unavailable for
        selected dates.
  \item \textbf{Booking Detail Drawer} — Click any slot to view full client details,
        contact information, and service requested.
\end{itemize}

\subsection{Customer Booking Portal}

A sleek, mobile-first web application allowing clients to:

\begin{enumerate}[leftmargin=2em]
  \item Browse available stylists and their profiles.
  \item Select a service from the salon's service menu.
  \item Choose a preferred date and available 30-minute time slot.
  \item Enter their name, contact number, and any notes.
  \item Receive instant confirmation via SMS/WhatsApp.
\end{enumerate}

\subsection{Automated Communication}

Integration with SMS and messaging gateways to deliver automated notifications:

\begin{itemize}[leftmargin=2em]
  \item \textbf{Booking Confirmation} — Sent immediately after a booking is created.
  \item \textbf{24-Hour Reminder} — Sent the day before the appointment.
  \item \textbf{2-Hour Reminder} — Sent two hours before the scheduled time.
  \item \textbf{Cancellation Notice} — Sent if a booking is cancelled by the salon.
\end{itemize}

SMS gateway: \textbf{Notify.lk} (Phase 1). WhatsApp Business API (Phase 2).

\subsection{QR Code Marketing}

A uniquely generated QR code per salon that links directly to the Customer Booking
Portal. The QR code can be:

\begin{itemize}[leftmargin=2em]
  \item Printed and displayed at the salon front desk.
  \item Added to business cards, flyers, and social media.
  \item Embedded in promotional materials.
\end{itemize}

This converts every physical visit into a digital relationship, building a loyal
customer database over time.

\subsection{Secure Authentication}

A professional login system powered by \textbf{AWS Cognito}:

\begin{itemize}[leftmargin=2em]
  \item Email/password login for salon admin accounts.
  \item Secure session management with JWT tokens.
  \item "Forgot Password" self-service flow with email verification.
  \item Multi-factor authentication (MFA) ready for Phase 2.
\end{itemize}

% ══════════════════════════════════════════════════════════════════════════════
\chapter{Technical Architecture}

\section{Technology Philosophy}

SalonSync follows a \textbf{Serverless-First} architecture to achieve:

\begin{itemize}[leftmargin=2em]
  \item \textbf{99.9\% uptime} with no server maintenance burden.
  \item \textbf{Near-zero idle cost} — infrastructure charges only apply when
        functions are actively invoked.
  \item \textbf{Automatic scaling} from 1 salon to 10,000 salons without code changes.
\end{itemize}

\section{Phase 1 Technology Stack}

\begin{longtable}{>{\bfseries}p{4cm} p{4.5cm} p{5cm}}
  \toprule
  \textbf{Layer} & \textbf{Technology} & \textbf{Purpose} \\
  \midrule
  \endfirsthead
  \toprule
  \textbf{Layer} & \textbf{Technology} & \textbf{Purpose} \\
  \midrule
  \endhead
  \bottomrule
  \endfoot

  Frontend          & React.js + Tailwind CSS     & Modern, responsive UI for both portals \\[4pt]
  Hosting           & AWS Amplify                 & CI/CD pipeline + CDN for global delivery \\[4pt]
  API Layer         & Amazon API Gateway          & RESTful API routing to Lambda functions \\[4pt]
  Backend           & Node.js on AWS Lambda       & Serverless business logic execution \\[4pt]
  Database          & AWS DynamoDB                & High-performance NoSQL with Single Table Design \\[4pt]
  Authentication    & AWS Cognito                 & Secure admin login, sessions, password reset \\[4pt]
  File Storage      & AWS S3                      & Salon logos and stylist profile photos \\[4pt]
  Messaging         & Notify.lk SMS Gateway       & Automated appointment reminders \\[4pt]
  Dev Environment   & Google Antigravity          & Agentic IDE for rapid development \\[4pt]
  Version Control   & GitHub                      & Source code management and collaboration \\
\end{longtable}

\section{System Architecture Diagram}

\begin{verbatim}
 ┌─────────────────────────────────────────────────────────────┐
 │                        CLIENTS                              │
 │         Browser / Mobile (React.js + Tailwind CSS)          │
 │   [Customer Booking Portal]   [Admin Dashboard]             │
 └──────────────────────┬──────────────────────────────────────┘
                        │  HTTPS
 ┌──────────────────────▼──────────────────────────────────────┐
 │                   AWS Amplify (CDN + Hosting)                │
 └──────────────────────┬──────────────────────────────────────┘
                        │
 ┌──────────────────────▼──────────────────────────────────────┐
 │              Amazon API Gateway (REST API)                   │
 │         /bookings   /stylists   /admin   /auth               │
 └──────┬───────────────┬───────────────┬────────────────┬─────┘
        │               │               │                │
 ┌──────▼──────┐ ┌──────▼──────┐ ┌─────▼──────┐ ┌──────▼──────┐
 │  Lambda:    │ │  Lambda:    │ │  Lambda:   │ │  Lambda:    │
 │  Booking    │ │  Stylist    │ │  Admin     │ │  Reminders  │
 │  Engine     │ │  Manager   │ │  Manager   │ │  (Async)    │
 └──────┬──────┘ └──────┬──────┘ └─────┬──────┘ └──────┬──────┘
        │               │               │                │
 ┌──────▼───────────────▼───────────────▼────────────────▼─────┐
 │                    AWS DynamoDB                              │
 │              (Single Table Design — PK/SK)                   │
 └──────────────────────────────────────────────────────────────┘
        │                                         │
 ┌──────▼──────┐                         ┌────────▼────────┐
 │ AWS Cognito │                         │  Notify.lk API  │
 │  (Auth)     │                         │  (SMS Gateway)  │
 └─────────────┘                         └─────────────────┘
\end{verbatim}

\section{DynamoDB Single Table Design}

All entities are stored in a single DynamoDB table using composite keys for
efficient access patterns.

\begin{longtable}{p{3.5cm} p{3.5cm} p{3cm} p{4cm}}
  \toprule
  \textbf{PK (Partition Key)} & \textbf{SK (Sort Key)} & \textbf{Entity} & \textbf{Access Pattern} \\
  \midrule
  \endfirsthead
  \toprule
  \textbf{PK} & \textbf{SK} & \textbf{Entity} & \textbf{Access Pattern} \\
  \midrule
  \endhead
  \bottomrule
  \endfoot

  \texttt{SALON\#\{id\}}        & \texttt{PROFILE}                        & Salon         & Get salon details \\[4pt]
  \texttt{STYLIST\#\{id\}}      & \texttt{PROFILE}                        & Stylist       & Get stylist profile \\[4pt]
  \texttt{STYLIST\#\{id\}}      & \texttt{SLOT\#\{date\}\#\{time\}}       & Slot          & Get slots by stylist+date \\[4pt]
  \texttt{BOOKING\#\{id\}}      & \texttt{DETAILS}                        & Booking       & Get booking by ID \\[4pt]
  \texttt{CUSTOMER\#\{phone\}}  & \texttt{BOOKING\#\{date\}}              & Customer      & Get customer history \\[4pt]
  \texttt{SALON\#\{id\}}        & \texttt{LEAVE\#\{stylistId\}\#\{date\}} & Leave         & Get leave by salon+date \\
\end{longtable}

% ══════════════════════════════════════════════════════════════════════════════
\chapter{Business Model}

\section{Pricing Strategy}

\begin{center}
\begin{tabular}{>{\centering}p{4cm} >{\centering}p{4cm} >{\centering\arraybackslash}p{4cm}}
  \toprule
  \textbf{Free Trial}     & \textbf{Basic Plan}            & \textbf{Pro Plan}             \\
  \midrule
  14 Days                 & 2,500 LKR/month                & 4,500 LKR/month               \\
  All features            & Up to 2 Stylists               & Up to 5 Stylists              \\
  No credit card          & SMS Reminders                  & WhatsApp Reminders            \\
  Full support            & Analytics Dashboard            & Priority Support              \\
  \bottomrule
\end{tabular}
\end{center}

\vspace{0.5cm}

\begin{infobox}[Note on Pricing]
Phase 1 launches with the Basic Plan only. The Pro Plan is introduced in Phase 2
once the product has been validated in the market.
\end{infobox}

\section{Revenue Projections}

\begin{longtable}{>{\bfseries}p{4cm} p{3cm} p{3cm} p{3.5cm}}
  \toprule
  \textbf{Milestone} & \textbf{Active Salons} & \textbf{Monthly Revenue} & \textbf{Annual Revenue} \\
  \midrule
  \endfirsthead
  \toprule
  \textbf{Milestone} & \textbf{Active Salons} & \textbf{Monthly Revenue} & \textbf{Annual Revenue} \\
  \midrule
  \endhead
  \bottomrule
  \endfoot

  Month 3   & 5   & 12,500 LKR    & —              \\[4pt]
  Month 6   & 20  & 50,000 LKR    & —              \\[4pt]
  Month 12  & 50  & 125,000 LKR   & 1,500,000 LKR  \\[4pt]
  Month 24  & 150 & 375,000 LKR   & 4,500,000 LKR  \\
\end{longtable}

\section{Cost Structure}

Estimated AWS monthly cost at 50 active salons:

\begin{itemize}[leftmargin=2em]
  \item \textbf{Lambda Invocations} — $\sim$\$2–5 USD/month
  \item \textbf{DynamoDB} — $\sim$\$1–3 USD/month (on-demand)
  \item \textbf{API Gateway} — $\sim$\$1–2 USD/month
  \item \textbf{Cognito} — Free (under 50,000 MAUs)
  \item \textbf{Amplify Hosting} — $\sim$\$1 USD/month
  \item \textbf{Total AWS Cost} — \textbf{Under \$12 USD/month}
\end{itemize}

This yields an estimated \textbf{gross margin above 95\%} at 50 subscribers.

% ══════════════════════════════════════════════════════════════════════════════
\chapter{Development Roadmap}

\section{Phase 1 — MVP (Months 1–3)}

\begin{longtable}{>{\bfseries}p{3cm} p{4cm} p{7cm}}
  \toprule
  \textbf{Sprint} & \textbf{Duration} & \textbf{Deliverables} \\
  \midrule
  \endfirsthead
  \toprule
  \textbf{Sprint} & \textbf{Duration} & \textbf{Deliverables} \\
  \midrule
  \endhead
  \bottomrule
  \endfoot

  Sprint 1 & Week 1–2 & Project setup, AWS infra, DynamoDB schema, Cognito auth \\[4pt]
  Sprint 2 & Week 3–4 & Booking engine (Lambda), slot management API, DynamoDB integration \\[4pt]
  Sprint 3 & Week 5–6 & Admin Dashboard UI (Grid View, manual bookings, leave management) \\[4pt]
  Sprint 4 & Week 7–8 & Customer Booking Portal (stylist selection, slot picker, confirmation) \\[4pt]
  Sprint 5 & Week 9–10 & SMS integration (Notify.lk), automated reminders, QR code generation \\[4pt]
  Sprint 6 & Week 11–12 & Testing, bug fixes, performance optimisation, beta launch \\
\end{longtable}

\section{Phase 2 — Growth (Months 4–6)}

\begin{itemize}[leftmargin=2em]
  \item WhatsApp Business API integration.
  \item Analytics dashboard (revenue, peak hours, stylist performance).
  \item Pro Plan launch (up to 5 stylists).
  \item Multi-salon architecture foundation.
  \item Staff mobile app (React Native).
\end{itemize}

\section{Phase 3 — Scale (Months 7–12)}

\begin{itemize}[leftmargin=2em]
  \item Full SaaS multi-tenancy rollout.
  \item Tiered subscription billing (Stripe or PayHere).
  \item Loyalty programme and client-facing mobile app.
  \item Franchise / chain salon support.
  \item API marketplace for third-party integrations.
\end{itemize}

% ══════════════════════════════════════════════════════════════════════════════
\chapter{Risk Analysis}

\begin{longtable}{>{\bfseries}p{4cm} p{3cm} p{7cm}}
  \toprule
  \textbf{Risk} & \textbf{Severity} & \textbf{Mitigation Strategy} \\
  \midrule
  \endfirsthead
  \toprule
  \textbf{Risk} & \textbf{Severity} & \textbf{Mitigation Strategy} \\
  \midrule
  \endhead
  \bottomrule
  \endfoot

  Low adoption by salon owners       & High   & Offer free onboarding support; use QR demo in-person at salons. \\[6pt]
  Double-booking race conditions     & High   & Use DynamoDB conditional writes (atomic transactions) for slot locking. \\[6pt]
  AWS cost overrun                   & Medium & Set billing alerts and Lambda concurrency limits from day one. \\[6pt]
  SMS gateway downtime               & Medium & Implement fallback to email; monitor Notify.lk SLA. \\[6pt]
  WhatsApp API policy changes        & Medium & Keep SMS as primary channel; WhatsApp as optional add-on. \\[6pt]
  Data privacy / GDPR compliance     & Medium & Store only essential PII; implement data deletion on request. \\[6pt]
  Competitor entry                   & Low    & Focus on hyper-local relationships and LKR pricing advantage. \\
\end{longtable}

% ══════════════════════════════════════════════════════════════════════════════
\chapter{Team \& Responsibilities}

\begin{longtable}{>{\bfseries}p{4cm} p{4cm} p{6cm}}
  \toprule
  \textbf{Role} & \textbf{Assigned To} & \textbf{Key Responsibilities} \\
  \midrule
  \endfirsthead
  \toprule
  \textbf{Role} & \textbf{Assigned To} & \textbf{Key Responsibilities} \\
  \midrule
  \endhead
  \bottomrule
  \endfoot

  Project Lead / Architect  & JDJ Solutions     & System design, AWS infrastructure, code review \\[4pt]
  Frontend Developer         & TBD               & React.js UI, Tailwind CSS, Amplify deployment \\[4pt]
  Backend Developer          & TBD               & Lambda functions, DynamoDB, API Gateway \\[4pt]
  QA Engineer                & TBD               & Test coverage, end-to-end testing, UAT \\[4pt]
  Sales \& Onboarding        & TBD               & Salon acquisition, free trial onboarding \\
\end{longtable}

% ══════════════════════════════════════════════════════════════════════════════
\chapter{Conclusion}

SalonSync represents a compelling opportunity to modernise the Sri Lankan salon
industry with a purpose-built, cost-effective, and technically robust platform.
By combining a serverless AWS architecture with a deeply empathetic product design
for non-technical salon owners, the project is positioned to become the de-facto
booking solution for independent salons across the country.

The phased approach ensures that every line of code written in Phase 1 contributes
to a scalable, maintainable foundation that can grow to serve hundreds of salons
without a fundamental re-architecture.

\begin{infobox}[Next Steps]
\begin{enumerate}
  \item Finalise DynamoDB schema design.
  \item Provision AWS environment (Amplify, API Gateway, DynamoDB, Cognito).
  \item Begin Sprint 1 development.
  \item Identify one pilot salon for beta testing.
\end{enumerate}
\end{infobox}

\vspace{1cm}
\begin{center}
  {\large\bfseries\color{primary} Ready to build. Ready to scale.}\\[0.3cm]
  {\color{accent} \rule{8cm}{1.5pt}}\\[0.5cm]
  {\normalsize JDJ Solutions — \textit{April 2026}}
\end{center}

% ══════════════════════════════════════════════════════════════════════════════
\end{document}
